iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-28 manuscript/main.tex
web page

\section*{Use cases} % FM: used often in other software articles in F1000res
To demonstrate the functionalities and flexibility of the iSEE package, we applied our method to a number of publicly available data sets.
Details are provided in the tour subfolder of the GitHub repository for this manuscript (\url{https://github.com/LTLA/iSEE2018}), and for each data set a combination of \_app.R and \_tour.txt is provided.
An instance of iSEE running on the respective data sets is provided as a stand-alone webpages, for demonstration purposes without the need for any software installation.

>>>>

\section*{Use cases} % FM: used often in other software articles in F1000res
To demonstrate the functionalities and flexibility of the iSEE package, we applied our method to a number of publicly available data sets.
Details are provided in the tour subfolder of the GitHub repository for this manuscript (\url{https://github.com/LTLA/iSEE2018}), and for each data set a combination of \_app.R and \_tour.txt is provided.
An instance of iSEE running on the respective data sets is provided as a stand-alone web pages, for demonstration purposes without the need for any software installation.
